Plant Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging

### 2022-11-27 script/manuscript_MEE.Rmd
some numbers to add

>>>>

XX corbiculae loads had DNA extracted and underwent hyb-seq, a total of XX corbiculae samples were sequenced, XX reads were recovered from sequencing. After trimming XX seqs remained. XX reads were matched using Kraken, of the reads classified by Kraken XX reads were matched using Bracken, of the reads classified by Kraken XX reads were matched using BLAST. The number of reads per sequence varied widely (min = , $\bar{x}$, max = ), the number of loci recovered per sample ranged from (min = , max = ), and the number of reads from loci also ranged widely ().
